Okay, so let's say you have two species.
There are four possible assemblages (one where both species are present, one where both species are absent, and two where one species is present and the other is absent).
Our goal is to determine how likely each of these four scenarios is.
For mathematical convenience, let's say that we fit an SDM for each species, and both came back saying that their species had a 50% probability of being present/observed at some site.

**A.** If we "stack" the two models by combining their probabilities independently, as suggested in [refs], then we would predict that each of the four possible assemblages are equally likely.

**B** If we relax the independence assumption, then 


```{r A}
library(MASS)
set.seed(1)

n = 1E6
SigmaB = matrix(c(0.75, 0, 0, 0.75), nrow = 2)

# maximum observed covariance in a set of predictions I found
SigmaC = matrix(c(4.63662276817617, 5.17744184924266, 5.17744184924266, 
5.84230112756645), nrow = 2)

p.list = list(
  B = plogis(mvrnorm(n, c(0, 0), SigmaB)),
  C = plogis(mvrnorm(n, c(0, 0), SigmaC))
)

species.names = list(
  B = c("Sora", "American Coot"),
  C = c("Sora", "American Coot")
)

n.panels = length(p.list)

pdf("a.pdf", height = 5 * 2/3, width = 5)
par(mfrow = c(n.panels, 3))
par(mar = c(4, 5, 2, 1) + .1)

boxprobs = function(x){
  matrix(
    c(
      both = mean(x[,1] * x[,2]),
      first = mean((1-x[,1]) * x[,2]),
      second = mean(x[,1] * (1-x[,2])),
      neither = mean((1-x[,1]) * (1-x[,2]))
    ),
    nrow = 2,
    ncol = 2
  )
}


for(i in 1:n.panels){
  # Top panel: monte carlo points
  plot(
    p.list[[i]][1:250, ], 
    xlim = c(0,1), 
    ylim = c(0,1.04), 
    asp = 1, 
    pch = 16, 
    col = "#00000025", 
    main = if(i ==1){"A"}else{NULL}, 
    xlab = paste0("P(",species.names[[i]][1], ")"), 
    ylab = paste0("P(",species.names[[i]][2], ")"), 
    xaxs = "i", 
    yaxs = "i",
    cex = .75, 
    mgp = c(2, 0.75, 0),
    axes = FALSE
  )
  axis(1, c(0, 1/2, 1))
  axis(2, c(0, 1/2, 1))
  points(.5, .5, pch = "+", cex = 2)
  
  # Middle panel: boxes
  plot(
    p.list[[i]], 
    xlim = c(0,1), 
    ylim = c(0,1), 
    asp = 1, 
    type = "n", 
    axes = FALSE, 
    xlab = paste0("No         Yes\n",species.names[[i]][1], " observed"), 
    ylab = paste0(species.names[[i]][2], " observed\nNo         Yes"), 
    main = if(i ==1){"B"}else{NULL}, 
    xaxs = "i", 
    yaxs = "i",
    mgp = c(1, 0, 0)
  )
  abline(v = .5, h = .5)
  abline(v = c(0, 1), h = c(0, 1))
  text(.75, .75, labels = round(boxprobs(p.list[[i]])[1], 2), cex = 2.5 * sqrt(boxprobs(p.list[[i]])[1]))
  text(.75, .25, labels = round(boxprobs(p.list[[i]])[2], 2), cex = 2.5 * sqrt(boxprobs(p.list[[i]])[2]))
  text(.25, .75, labels = round(boxprobs(p.list[[i]])[3], 2), cex = 2.5 * sqrt(boxprobs(p.list[[i]])[3]))
  text(.25, .25, labels = round(boxprobs(p.list[[i]])[4], 2), cex = 2.5 * sqrt(boxprobs(p.list[[i]])[1]))
  
  # Bottom panel: richness
  barplot(
    names.arg = 0:2,
    c(
      boxprobs(p.list[[i]])[4], 
      sum(boxprobs(p.list[[i]])[2:3]), 
      boxprobs(p.list[[i]])[1]
      ),
    ylim = c(0, .5),
    ylab = "probability",
    xlab = "richness",
    axes = FALSE,
    mgp = c(2.25, 1, 0),
    main = if(i ==1){"C"}else{NULL}, 
  )
  axis(2, c(0, 1/4, 1/2))
}
dev.off()


par(mfrow = c(1,1))
```

```{r real-model}
set.seed(NULL)
i = sample.int(nrow(prediction.array), 1)
covs = cov(t(prediction.array[i, , ]))
dimnames(covs) = list(colnames(route.presence.absence), colnames(route.presence.absence))
sp.1 = which.min(covs[cbind(1:368, apply(covs, 1, which.min))])
sp.2 = which.min(covs[, sp.1])

spp = c(sp.1, sp.2)

sp.covs = covs[, spp[1]]
sp.covs[spp] = 0
sp.3 = which.max(abs(sp.covs))

p = t(prediction.array[i,spp,])
colnames(p) = colnames(route.presence.absence)[spp]

weights = prediction.array[i,sp.3,] / sum(prediction.array[i,sp.3,])
areas = weights
radii = sqrt(areas * nrow(p))
cex = .4

par(mfrow = c(1, 2))
plot(p, xlim = c(0,1), ylim = c(0,1), asp = 1, pch = 16, col = "#00000050",
     main = "baseline samples", cex = cex)
points(mean(p[,1]), mean(p[,2]), pch = "*", cex = 3, col = 2)

plot(p, xlim = c(0,1), ylim = c(0,1), asp = 1, cex = radii * cex, pch = 16, col = "#00000050", main = paste("samples given known\n", colnames(route.presence.absence)[sp.3]))
arrows(
  x0 = mean(p[,1]), y0 = mean(p[,2]),
  x1 = sum(p[,1] * weights), y1 = sum(p[,2] * weights), 
  col = "red",
  lwd = 4,
  length = .2
)
par(mfrow = c(1, 1))

colMeans(p) - colSums(p * weights)

```

